---
title: "Multivariate trend tests"
author: "Dorsaf Goutali"
date: '2024-01-30'

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

The document is a technical guide for a code designed to calculate and compare the performance of four different tests used for detecting trends in multivariate data seriesfod different scenarios. These tests include (MOT/MDT) and (CET/CIT). 

#run all function:Power evaluation_ trend tests_Margins,
#Power evaluation_tests_Dependence_Margins,
#Power evaluation_trend_Dependence,P-value,Statistique_tests,excel_setup
```{r}
excel_setup = function(Dir){
  
  setwd(Dir)
  
  # loader des packages necessaires:
  RequiredPackages <- c("copula","Kendall","VGAM","gtools","openxlsx",
                        "resample","openxlsx","foreach",
                       "MASS")
  
  for (i in RequiredPackages) { 
    if (!require(i, character.only = TRUE)) require(i)
  }
  
  row_names = t(c("","MDT","MOT","CIT","CET"))
  col_name = paste("% p.val < alpha",sep="")
  
  compare = createWorkbook()
  addWorksheet(compare,sheetName="test_power")
  
  writeData(compare,sheet="test_power",x=row_names,colNames = FALSE,rowNames = FALSE)
  writeData(compare,sheet="test_power",x=col_name,colNames = FALSE,rowNames = FALSE,startRow = 2)
  
  top_row_style = createStyle(border="bottom",borderStyle="thick",textDecoration = "bold")
  addStyle(compare,"test_power",style=top_row_style,rows=1,cols=1:4)
  addStyle(compare,"test_power",style=createStyle(textDecoration = "bold",),rows=2:50,cols=1)
  
  saveWorkbook(compare,file="COMPARE.xlsx",overwrite = TRUE)

}
excel_setup("directory")
```


# Example : No trend under_H0(tau:0.2, copula:clayton,n=30)

```{r}
Trend_tests(run_num = 1,copula = "clayton",coefs = rep(0.2,30),Nsim = 1000,Nbs = 1000,width = 10,alpha = 0.05)
```

## Trend in Dependence structure (copula:clayton,n=30)

```{r}

Trend_tests (run_num = 1,copula = "clayton",coefs =seq(0,1,length.out=30), Nsim = 1000, Nbs=1000, width = 10, alpha = 0.05) 
```

# Trend in one Margins(copula:galambos,tau:0.6,n=50,trend in one margin:0.3)

```{r}
Perfermance_tests_margins(run_num = 1,copula = "galambos",coefs = rep(0.2,50),Nsim = 1000,Nbs = 1000,width = 15,alpha = 0.05,location_param_x = 0.3,location_param_y = 0.3,trend_in_margin = "margin_1")
```

# Trend in both Margins(copula:galambos,tau:0.6,n=50,trend in both margins:0.3)
```{r}
Perfermance_tests_margins(run_num = 1,copula = "galambos",coefs = rep(0.2,50),Nsim = 1000,Nbs = 1000,width = 15,alpha = 0.05,location_param_x = 0.3,location_param_y = -0.1,trend_in_margin = "both")
```
#Trend in Dependence and in both Margins(copula:clayton,n=30,trend in both margins:-0.1)

```{r}
Power_tests_Dependence_Margins(run_num = 1,copula = "clayton",coefs = seq(0,1,length.out=30),Nsim = 1000,Nbs = 1000,width = 10,alpha = 0.05,location_param_x = -0.1,location_param_y = -0.1)
```

